---
title: "Viewing Your daff"
author: "Kent Russell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Viewing daff}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The first purpose of this vignette is to test the functionality of `render_diff` in a `rmarkdown` document.  As of version 0.1.4, `daff` had really no support for rendering in `rmarkdown`.  Going forward though, using `htmltools` from RStudio should allow us to integrate seamlessly into `rmarkdown`.

Let's see if the change works.

### Does It Work?

```{r results='asis'}
library(daff)

y <- iris[1:3,]
x <- y

x <- head(x,2) # remove a row
x[1,1] <- 10 # change a value
x$hello <- "world"  # add a column
x$Species <- NULL # remove a column

patch <- diff_data(y, x)
render_diff(patch, fragment = F)
```

Now with `fragment = TRUE`, which is the default.  I wonder if it should now be `FALSE`.

```{r}
library(daff)

y <- iris[1:3,]
x <- y

x <- head(x,2) # remove a row
x[1,1] <- 10 # change a value
x$hello <- "world"  # add a column
x$Species <- NULL # remove a column

patch <- diff_data(y, x)
render_diff(patch, fragment = T)
```
